### 2022-04-10 manuscript.tex
sunday [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/eaf13b4469216af1bafbda0b8626cd110d0b56cf.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/eaf13b4469216af1bafbda0b8626cd110d0b56cf/checks
https://github.com/scherzerthesis/thesis/actions/runs/2144492858

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/a8b484c207053ab9518e450fd19345960cfa9065/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/a8b484c207053ab9518e450fd19345960cfa9065}{scherzerthesis/thesis@a8b484c}
on April 9, 2022.

@@

@@

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/eaf13b4469216af1bafbda0b8626cd110d0b56cf/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/eaf13b4469216af1bafbda0b8626cd110d0b56cf}{scherzerthesis/thesis@eaf13b4}
on April 10, 2022.

@@

\hypertarget{materials-and-methods}{%
\subsection{Materials and Methods}\label{materials-and-methods}}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1624}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1709}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2308}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1368}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2991}}@{}}
\caption{\textbf{Critical reagents} \label{tbl:reagents}}\tabularnewline
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Reagents List}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Reagent Type
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Name
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Source
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Catalog number
\end{minipage} \\
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Reagents List}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Reagent Type
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Name
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Source
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Catalog number
\end{minipage} \\
\midrule
\endhead
antibody & beta-Actin & CST & 3700T & wb: 1:10,000 \\
antibody & Phospho ERK1/2 & CST & 4370 & wb:1:2000, IHC:1:1000 \\
antibody & ERK1/2 & CST & 4696 & wb: 1:2000 \\
antibody & P53 & Leica & cm-5 & wb: 1:2000, IHC: 1:1000, IF:1:250 \\
antibody & NKX2-1 & Abcam & ab76013 & IHC: 1:1000 \\
antibody & Pro-SPC & Millipore & Cat\# AB3786 & IHC: 1:2000 \\
antibody & HMGA2 & CST & 8179S & IHC 1:2000 \\
antibody & p19/ARF & Chuck Sherr & (Bertwistle et al., 2004) & \\
Cell Line & 293T & ATCC & CRL-3216 & \\
Cell Line & HCC-364 & Bivona lab & (Lin et al., 2014) & \\
Recombinant DNA & Pmd2.g & Addgene & \#12259 & \\
Recombinant DNA & pspax2 & Addgene & \#12260 & \\
Recombinant DNA & P53-R175H & Addgene & \#22936 & \\
Chemical Compound & dabrafenib & Selleck & S2807 & \\
Chemical Compound & PLX4720 & Plexxikon/ Research Diets & & \\
Chemical Compound & trametinib & Selleck & S2673 & \\
Other & Collagenase type 1 & Thermo Fischer Scientific & 17100017 & \\
Other & Dispase & Corning & 354235 & \\
other & Elastase & Worthington Biochem & LS006365 & \\
other & ad5spc-Cre & university of Iowa & VVC-Berns1168 & \\
\bottomrule
\end{longtable}

@@

\leavevmode\vadjust pre{\hypertarget{ref-18dmdoj17}{}}%
Bertwistle, D., Zindy, F., Sherr, C.J., and Roussel, M.F. (2004). Monoclonal antibodies to the mouse p19(Arf) tumor suppressor protein. Hybrid Hybridomics \emph{23}, 293--300. \url{https://doi.org/10.1089/hyb.2004.23.293}.
